A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-08-11 manuscript.tex

% formatting links in the PDF file
\definecolor{myurlcolor}{HTML}{1a0dab}
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = myurlcolor, %blue,Colour for external hyperlinks
linkcolor    = black, %blue, Colour of internal links
citecolor   = black, % cyan, Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

@@

% Authors
\author[*,1]{Jannis Kreienkamp}
\author[1]{Maximilian Agostini}
\author[1]{Kai Epstude}
\author[2]{Rei Monden}
\author[1,3]{Peter de Jonge}
\author[1,3]{Laura F. Bringmann}
\affiliation{\hfill}

>>>>

% formatting links in the PDF file
\definecolor{googleurlcolor}{HTML}{1a0dab}
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = googleurlcolor, %blue,Colour for external hyperlinks
linkcolor    = black, %blue, Colour of internal links
citecolor   = black, % cyan, Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

@@

% Authors
\author[*,1]{Jannis Kreienkamp}
\author[1]{Maximilian Agostini}
\author[2]{Rei Monden}
\author[1]{Kai Epstude}
\author[1,3]{Peter de Jonge}
\author[1,3]{Laura F. Bringmann}
\affiliation{\hfill}
